Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-08-17 manuscript/main.tex
draft done!!!

		\begin{abstract}
		Modern biomedical studies are increasingly collecting both functional and vector-valued predictors for each subject, introducing the new challenge of cross-modality correlations. To address this, we propose a hybrid partial least squares (PLS) regression framework that integrates functional and scalar predictors within a unified Hilbert space.
		We then extend the classical nonlinear iterative PLS (NIPALS) algorithm to this hybrid Hilbert space by iteratively maximizing the empirical cross-covariance with the response. As a result, our method identifies low-dimensional directions that capture both within- and between-modality variation, as well as the response-predictor correlation. The procedure is computationally efficient, requiring only the solution of linear systems at each step. We provide theoretical properties to justify our algorithm and demonstrate its effectiveness through simulations and an application to clinical outcome prediction using renal imaging and scalar covariates from the Emory University renal study.
		\end{abstract}

>>>>

		\begin{abstract}
			Modern biomedical studies are increasingly collecting both functional and vector-valued predictors for each subject, introducing the new challenge of cross-modality correlations. To address this, we propose a hybrid partial least squares (PLS) regression framework that integrates functional and scalar predictors within a unified Hilbert space.
			We then extend the classical nonlinear iterative PLS (NIPALS) algorithm to this hybrid Hilbert space by iteratively maximizing the empirical cross-covariance between the hybrid predictor and the response. As a result, our method identifies low-dimensional representations that capture both within- and between-modality variation, as well as the response-predictor correlation. The procedure is computationally efficient, requiring only the solution of linear systems at each step. We provide theoretical properties to justify our algorithm and demonstrate its effectiveness through simulations and an application to clinical outcome prediction using renal imaging and scalar covariates from the Emory University renal study.
		\end{abstract}
